Summary Statistics

### 2024-12-17 extensive_tests/draft-sumstat-vignette.Rmd
Updating changes
Updating sumstats and test sumstats
Updating work on siteFChange

---
title: "Summary Statistics"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to MethEvolSIM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

get_FChange_cherryData (uses find_cherries and cherry_diffs)

>>>>

---
title: "Summary Statistics"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Summary Statistics with MethEvolSIM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

We calculate the frequency of sites that changes for each structure.

get_FChange_cherryData (uses find_cherries --get_cherryDist-- and cherry_diffs -- now count_cherryMethDiff )

NOTE: Summary statistics related with tree cherries will require a
